多變量分析 HW3

### 2018-05-05 1062_class/Multivariate_Analysis/HW3_factor_analysis/HW3.Rmd
up

```{r setup, include=FALSE}
if (knitr::is_html_output()) {
    knitr::opts_chunk$set(echo = FALSE,
                          message=FALSE,
                          warning=FALSE,
                          comment = "",
                          dev='svg',
                          fig.dim=c(3.6, 3.2))
} else {
    knitr::opts_chunk$set(echo = FALSE,
                          message=FALSE,
                          warning=FALSE,
                          comment = "",
                          out.width = '70%',
                          out.height = '5.5cm')
}
options(digits = 4)
library(readr)
library(tidyverse)
library(knitr)
library(kableExtra)
library(mat2tex)
theme <- theme(axis.text.x = element_text(size = 7, face = "plain", angle = 30),
               axis.text.y = element_text(size = 7, face = "plain"),
               axis.title.x = element_text(size = 9, face = "bold"),
    axis.title.y = element_text(size = 9, face = "bold"))
source("multivariate_fc.R")
```

@@

Q2: 9.32
====================================
```{r}
library(readr)
library(psych)
bulls <- read_table2("T1-10.dat", col_names = FALSE)
colnames(bulls) <- c("Breed", "SalePr", "YrHgt", 
                     "FtFrBody", "PrctFFB", "Frame",
                     "BkFat", "SaleHt", "SaleWt")
bulls <- bulls[,-c(1,9)]
```

### (a) S PC
```{r}
fa_3 <- fa(cov(bulls), nfactors=3, rotate="varimax", covar = T, fm="pa", scores="regression")
#no principle component method
```

### (b) S MLE

```{r}
fa_3 <- fa(cov(bulls), nfactors=3, rotate="varimax", covar = T, fm="ml", scores="regression")
```

@@

```{r}
fa_3 <- fa(cov(bulls), nfactors=3, rotate="varimax", covar = T, fm="pa", scores="regression")
#no principle component method
```

### (d) R MLE
```{r}
fa_1 <- factanal(bulls, factors = 1, scores = "regression", rotation = "varimax")
fa_2 <- factanal(bulls, factors = 2, scores = "regression", rotation = "varimax")
fa_3 <- factanal(bulls, factors = 3, scores = "regression", rotation = "varimax")
```

@@

```{r}
library(psych)
items <- drinks[,-(1:2)]
fa(cov(items), nfactors=3, rotate="varimax", covar = F, fm="pa", scores="regression")
```

>>>>

```{r setup, include=FALSE}
if (knitr::is_html_output()) {
    knitr::opts_chunk$set(
	echo = FALSE,
	fig.dim = c(3.6, 3.2),
	message = FALSE,
	warning = FALSE,
	comment = "",
	dev = "svg",
	out.width = "70%"
)
} else {
    knitr::opts_chunk$set(echo = FALSE,
                          message=FALSE,
                          warning=FALSE,
                          comment = "",
                          out.width = '70%')
}
options(digits = 4)
library(readr)
library(tidyverse)
library(knitr)
library(kableExtra)
library(mat2tex)
theme <- theme(axis.text.x = element_text(size = 7, face = "plain", angle = 30),
               axis.text.y = element_text(size = 7, face = "plain"),
               axis.title.x = element_text(size = 9, face = "bold"),
    axis.title.y = element_text(size = 9, face = "bold"))
source("multivariate_fc.R")
```

@@

Q2: 9.32
====================================
```{r}
library(readr)
library(psych)
bulls <- read_table2("T1-10.dat", col_names = FALSE)
colnames(bulls) <- c("Breed", "SalePr", "YrHgt", 
                     "FtFrBody", "PrctFFB", "Frame",
                     "BkFat", "SaleHt", "SaleWt")
bulls <- bulls[,-c(1,9)]
source("fa_functions.R") # for formating loading mt
```

### (a) S PC
```{r}
fa_S_pc <- principal(bulls, 
              nfactors = 2, 
              rotate = 'varimax', 
              covar = TRUE)
fa_S_pc[["loadings"]][,] %>% round(3) %>%
    format_loading_matrix(criterion = 30, markdown = T) %>%
    kable("markdown",align = 'c', escape = F)
```

### (b) S ML

```{r}
fa_S_ml <- fa(bulls, nfactors=2, 
              rotate="varimax", covar = T,
              fm="ml", scores="regression")
fa_S_ml[["loadings"]][,] %>% round(3) %>%
    format_loading_matrix(criterion = 30, markdown = F) %>%
    kable("html",align = 'c', escape = F)
```

@@

```{r}
fa_R_pc <- principal(bulls, 
              nfactors = 2, 
              rotate = 'varimax', 
              covar = F)
fa_R_pc[["loadings"]][,]
```

### (d) R ML
```{r}
fa_R_ml <- fa(bulls, nfactors=2, 
              rotate="varimax", covar = F, 
              fm="ml", scores="regression")
fa_R_ml[["loadings"]][,]
```

@@

```{r}
library(psych)
items <- drinks[,-(1:2)]
```
